Improved Bounds for Online Balanced Repartitioning

### 2020-04-20 paper/waoa20clustering.tex
Comments
k=2 proof sketch

\usepackage{balance}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{amsthm,amsmath,amssymb,array,colortbl,graphicx,multirow}
\usepackage{comment}
\usepackage{balance}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{patterns} %
\usepackage{algorithm}
\usepackage[font={footnotesize}]{subcaption}
\usepackage[font={footnotesize}]{caption}
\usepackage{breakcites}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{cleveref}
\usepackage{enumitem}

@@

@@

@@

Now, we claim that the cost of node migration of \OFF is $2 \cdot \alpha$ (two caching nodes are swapped) if $\OPT$ performs a fetch, and 0 if
$\OPT$ does not change its cache contents.
Within each type of configuration with $S \in \{ B, C\}$ split, $\OPT$ may achieve a configuration with a different node from $S$ outside of the cache by exchanging the split node with any node from $S$.
To transition between any of three configuration types ((1) with $A$ (2) with $B$ split and (3) with C split), it suffices to perform a single exchange.
Therefore, $\OFF(\comm_t(\sigma^P_t)) = 2 \cdot \alpha \cdot \OPT(\sigma^P_t)$, which summed over the entire sequence $\sigma^P$ yields $\OFF(\sigma^B) = 2 \cdot \alpha \cdot \OPT(\sigma^P)$.

@@

>>>>

\usepackage{balance}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{amsthm,amsmath,array,colortbl,graphicx,multirow}
\usepackage{comment}
\usepackage{balance}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{patterns} %
\usepackage{algorithm}
\usepackage[font={footnotesize}]{subcaption}
\usepackage[font={footnotesize}]{caption}
\usepackage{breakcites}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{cleveref}
\usepackage{enumitem}

@@

% for my small screen
\setlength{\textwidth}{8cm}

@@

\maciek{Let's follow the SIDMA notation here. For example, a "single" node (the one that belongs to singleton component) is called "trivial" there.}

@@

Now, we claim that the cost of node migration of \OFF is $2 \cdot \alpha$ (two caching nodes are swapped) if $\OPT$ performs a fetch, and 0 if
$\OPT$ does not change its cache contents.
Within each type of configuration with $S \in \{ B, C\}$ split, $\OPT$ may achieve a configuration with a different node from $S$ outside of the cache by exchanging the split node with any node from $S$.
To transition between any of three configuration types ((1) with $A$ (2) with $B$ split and (3) with C split), it suffices to perform a single exchange.
Therefore, $\OFF(\comm_t(\sigma^P_t)) = 2 \cdot \alpha \cdot \OPT(\sigma^P_t)$, which summed over the entire sequence $\sigma^P$ 5yields $\OFF(\sigma^B) = 2 \cdot \alpha \cdot \OPT(\sigma^P)$.

@@

Algorithm Alg:
maintain a counter $C_{\set{u,v}}$ for each pair of nodes $\set{u,v}$ and increment it on every remote request between $u$ and $v$.
Once $C_{\set{u,v}} = \lambda:=2\alpha$,
reset the counter and collocate the pair arbitrarily in one of the two clusters where $u$ or $v$ resides.

\begin{theorem}
	The algorithm is 4-competitive.
\end{theorem}
\begin{proof}
\mahmoud{still proof sketch}
We charge both OPT and Alg on each request that triggers a collocation.
Let $C^{t}_{\set{u,v}}$ denote the  value of $C_{\set{u,v}}$ immediately after arrival of $\sigma_t$.
Assume on request $\sigma_{t}=\set{u,v}$,
Alg collocates the pair,
which means $ C^t_{\set{u,v}} = \lambda$ immediately before Alg resets the counter.
Let $t''<t$ be the latest time (i.e.~request) when Alg collocates $\set{u,v}$ before $t$.
Let $t', t'' < t' < t$ be the  time when Alg separates $\set{u,v}$
in order to collocate some other pair sharing a node,
e.g., the pair $\set{u,v'}, v' \neq v$.
%e.g., the request $\sigma_{t'} = \set{u,v'}$.
%By Alg's definition,
%$C^{t'}_{\set{u,v'}}  = C^t_{\set{u,v}} = \lambda$.
We denote the set of all requests to $\set{u,v}$
between times $t'$ and $t$ by $\sigma_{\set{u,v}}[t',t]$.
Thus,
$| \sigma_{\set{u,v}}[t',t] | = \lambda$.
The overall cost of requests that increases the counter,
i.e.~requests in $\sigma_{\set{u,v}}[t',t]$,
and the moving cost incurred by Alg,
 is $\lambda + 2\alpha$.
%That is, the cost of all requests in $\sigma_{\set{u,v}}[t',t]$.
We distinguish three cases for the cost incurred by OPT with regards to $\set{u,v}$.
i)
OPT has $\set{u,v}$ separated through all requests in $\sigma_{\set{u,v}}[t',t]$
and therefore it pays $\lambda$.
ii)  
OPT collocates $\set{u,v}$ some time during $[t'',t]$.
Recall that whenever Alg collocates a pair,
we charge OPT only for requests up to that point (i.e., not for later requests).
Hence,
we charge the cost of  this collocation to OPT for the first time.
In particular,
we charge OPT the cost of moving one node to the cluster of the other,
e.g.~$u$ to $v$, w.l.o.g.
Therefore in this case OPT pays $\alpha$.
iii)
OPT has $\set{u,v}$ collocated before $t''$ and keeps them collocated during $[t'',t]$.
Obviously in this case OPT doesn't pays any cost for requests in $\sigma_{\set{u,v}}[t'',t]$.
However,
OPT must pay $\lambda$ for requests to $\set{u,v'}$.
By induction,
at time $t'$,
we charge OPT $\alpha$ (out of $\lambda=2\alpha$) for this pair.
Therefore,
we can charge OPT another $\alpha$ to account for requests $\sigma_{\set{u,v}}[t'',t]$.
It can be easily verified that any deviation from these cases only increases the cost to OPT.
Thus,
OPT pays at least $\alpha$ for each collocation by Alg
which gives the competitive ratio 
$(\lambda + 2\alpha)/ \alpha = 4$.

\end{proof}
